Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
Changing potential neighbours organisation

\newglossaryentry{convHull}
{
    name=convex hull,
    description={The smallest convex set containing a given set}
}

@@

\section{Finding potential neighbours}
\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each \acrfull{bs}.
Here are the different methods we can use to solve this problem:

@@

A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.

It can be associated with an unoriented graph $G = (P, U)$ where $U$ is composed of every edge of $D(P)$.
Therefore, it is often used as a method to detect the closest neighbors \cite{delaunay_neighbor} (each nodes that are considered neighbors are
connected by an edge in $G$).

@@

Formally, it is the graph $G$ with vertex set $S$ in which any two distinct points $p\in S$ and $q\in S$ are adjacent precisely when the closed disc having pq as a diameter contains no other points.

\subsection{$k$-NN graph}
\noindent Nevertheless, the two methods presented above are triangulation, that is to say that they do not connect each \acrshort{bs} to all of its potential neighbours.

One simple idea to get rid of this problem could be solved by connecting each \acrshort{bs} to its $k$ nearest neighbours.

@@

\bibliographystyle{IEEEtran}
\bibliography{./biblio.bib}

>>>>

@@

\section{Finding potential neighbours}
\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each \acrfull{bs}.
For that, we will construct a neigbouring graph $G = (P, U)$ (each base station that are considered neighbors are
connected by an edge) where $P$ is the set of all base stations. 
Here are the different methods we can build this graph with:

\subsection{$k$-NN graph}
\noindent The most intuitive method is to connect each \acrshort{bs} to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ 
is a parameter to be fixed.

However, this method can be criticized, because it always finds $k$ neighbor to each base stations, no matter the reality of the 
data.

@@

A Delaunay triangulation of a set of points in the plane subdivides their convex hull into triangles whose circumcircles 
do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.

A Voronoi diagram is a tessellation pattern in which $n$ points scattered on a plane subdivides in 
exactly $n$ cells enclosing a portion of the plane that is closest to each point.

The Delaunay triangulation is the pendant of the Voronoi diagram in the sense that two points are connected in the
Delaunay triangulation if their associated cells share an edge in the Voronoi diagram.

Therefore, another approach, consists in computing a Delaunay triangulation and build a neighouring graph $G = (P, U)$ where $U$ 
is composed of every edge of $D(P)$. Which is equivalent to consider two base station as potential neighbors if their associated
cells are touching each other in the Voronoi diagram.

This method has already been used in articles in the past \cite{delaunay_neighbor}.

@@

Formally, it is the graph $G = (P, U)$ in which any two distinct points $p, q \in P$ are adjacent precisely when the closed disc having $pq$ as a diameter contains no other points.

@@

\bibliographystyle{alpha}
\bibliography{./biblio.bib}
